---
title: "p8105_hw1_yu_yh3430"
author: Yu He
date: 2021-09-28
output:  github_document
   
---
Homework 1 for P8105 data science
By Yu He

## Homework 1 Question 1
Part 1 create data frame includes numeric, character, and factor variables

```{r }
library(tidyverse)

set.seed(123456789)

HW1_Q1 <- tibble(
  norm_var = rnorm(10),
  norm_var_pos = norm_var > 0,
  char_var = c("hello", "this", "is", "my", "first", "R", "programming", "class", "excellent", "experience"),
  fact_var = factor(c("a", "a", "b", "b", "c", "c", "a", "a", "b", "b"))
)
```

Part 2 take mean of each variable

```{r}
mean_norm_var = mean(pull(HW1_Q1, norm_var))
mean_norm_var_pos = mean(pull(HW1_Q1, norm_var_pos))
mean_char_var = mean(pull(HW1_Q1, char_var))
mean_fact_var = mean(pull(HW1_Q1, fact_var))
```

take mean results - the numeric and logic give us the mean value
the character and factor vector give us the warning message - argument is not numeric or logic

Part 3 take mean after applies the as.numeric function

```{r}
mean(as.numeric(pull(HW1_Q1, char_var)))
mean(as.numeric(pull(HW1_Q1, norm_var_pos)))
mean(as.numeric(pull(HW1_Q1, fact_var)))
```

The as.numeric function convert other type of variable to numeric variable

## Homework 1 Question 2
Part 1 load package and dataset 

```{r}
install.packages("palmerpenguins")
data("penguins", package = "palmerpenguins")
```

Part 2 description of penguins dataset
The summary of dataset penguins provides max, min, mean, median values for each values.
`r summary(penguins)`
The dataset includes `r nrow(penguins)` rows and `r ncol(penguins)` columns.
the mean value of flipper length is `r print(summary(penguins) [4, 5])`.

Part 3 scatterplot of flipper_length_mm (y) vs bill_length_mm (X), and save the scatterplot as pdf.
```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

ggsave("scatterplot_penguins.pdf")
```




